Partial MILP to improve $\alpha,\beta$-CROWN accuracy \\ for hard DNN verification instances

### 2024-09-16 ICLR25/Paper_noProof.tex
edit

\begin{abstract}
$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
trade-off between accuracy vs computational time. VNNcomp however is focusing on relatively easy verification instances (network, inputs (images)), 
with few {\em unstable nodes}. In this paper, we consider harder verification instances, namely the usual local robustness problem, and 
compare how different solutions out there fare. On such instances, $\alpha,\beta$-CROWN displays a large gap ($\approx 40\%$) between instances that can be verified, and instances with an explicit attack. Enabling much larger time-outs for $\alpha,\beta$-CROWN only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time. Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs (10000s per instance): They would theoretically be able to close the gap, but with an untractable runtime on all but small instances, because the instances considered are hard.

@@

	MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
	$\epsilon = 0.026$ &  &  & ? &  18s &  1600s  \\  \hline
    MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
	$\epsilon = 0.015$ & &  & ? &  17s &  ?s  \\  \hline
	MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
	$\epsilon = 0.026$ &  &  & ? &  20s &  ?s  \\  \hline
	MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
	$\epsilon = 0.015$ & &  & 7s &  s &  ?s  \\  \hline
	MNIST 6$\times$500 &  ? & 94\%  & 41\%  & 43\%  & 44\%   \\ 
	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
	CIFAR CNN-B-adv & ?  & 62\%  &  ? & 40\%  & 42\%   \\
	 &  &  & s & s & s  \\ \hline \hline
	CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
	Wong &  &  & 2s & 2s & 2s  \\ \hline

>>>>

\begin{abstract}
$\alpha,\beta$-CROWN has won the last 4 VNNcomp(etitions), as the DNN verifier with the best 
trade-off between accuracy vs computational time. VNNcomp however is focusing on relatively easy verification instances (network, inputs (images)), 
with few {\em unstable nodes}. In this paper, we consider harder verification instances, namely the usual local robustness problem, and 
compare how different solutions out there fare. On such instances, $\alpha,\beta$-CROWN displays a large gap ($20-58\%$) between instances that can be verified, and instances with an explicit attack. Enabling much larger time-outs for $\alpha,\beta$-CROWN only improves verification rate by few percents, leaving a large gap of undecided instances while already taking a considerable amount of time. Resorting to other techniques, such as complete verifiers, does not fare better even with very large time-outs (10000s per instance): They would theoretically be able to close the gap, but with an untractable runtime on all but small instances, because the instances considered are hard.

@@

	MNIST 6$\times$100 & 96\% & 90\% & 33\% & 35\% & 40\%   \\
	$\epsilon = 0.026$ &  &  & ? &  18s &  1600s  \\  \hline
    MNIST 6$\times$200 & 97\%  & 96\%  & 46\%  & 49\%  & 50\%   \\ 
	$\epsilon = 0.015$ & &  & ? &  17s &  ?s  \\  \hline
	MNIST 9$\times$100 & 95\%  & 86\%  & 23\%  & 28\%  & 28\%   \\
	$\epsilon = 0.026$ &  &  & ? &  20s &  ?s  \\  \hline
	MNIST 9$\times$200 & 95\%  & 91\%  & 35\%  & 36\%  & 37\%   \\ 
	$\epsilon = 0.015$ & &  & 7s &  s &  ?s  \\  \hline
	MNIST 6$\times$500 &  ? & 94\%  & 41\%  & 43\%  & 44\%   \\ 
	$\epsilon = 0.035$ & &  & 6s &  15s &  1002s  \\  \hline
	CIFAR CNN-B-adv & ?  & 62\%  &  40\% & 41\%  & 42\%   \\
	 &  &  & 15s & 32s & 373s  \\ \hline \hline
	CIFAR ResNet & 29\%  & 25\%  & 25\%  & 25\%  & 25\%   \\
	$\epsilon=2/255$ & : &  & 2s & 2s & 2s  \\ \hline
